---
title: "CrossR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

Cross-validation is an important technique used in model selection and hyper-parameter optimization. Scores from cross-validation are a good estimation of test score of a predictive model in test data or new data as long as the IID assumption approximately holds in data. This package aims to provide a standardized pipeline for performing cross-validation for different modeling functions in R. In addition, summary statistics of the cross-validation results are provided for users.  

The `CrossR` package (short for _Cross_-validation in _R_) is a set of functions for implementing cross-validation inside the R environment.  

### Similar packages

Cross-validation can be implemented with the [`caret`](https://cran.r-project.org/web/packages/caret/caret.pdf) package in R. `caret` contains the function `createDataPartition()` to split the data and `train_Control()` to apply cross-validation with different methods depending on the `method` argument. We have observed that `caret` functions have some features that make the cross-validation process cumbersome. `createDataPartition()` splits the *indices* of the data which could be used later on to actually split the data into training and test data. This will be applied with one step using `split_data()` in `CrossR`.


## Functions

Three main functions in `CrossR`:

- `train_test_split`: This function partitions data into `k`-fold and returns the partitioned indices. A random shuffling option is provided. (`stratification` option for imbalanced representations will also be included if time allows).

- `cross_validation`: This function performs `k`-fold cross validation using the partitioned data and a selected model. It returns the scores of each validation. Additional methods for corss validation will be implemented (such as "Leave-One-Out" if time allows).

- `summary_cv`: This function outputs summary statistics(mean, median, standard deviation) of cross-validation scores.


## Usage

For installation of this package:
```{r}
devtools::install_github("UBC-MDS/CrossR")
```

Usage examples:

```{r}
library(CrossR)

data <- gen_data(100)
X <- data.frame(data[[1]])
y_vec <- data[[2]]
y <- data.frame(y = y_vec)

split_data <- train_test_split(X, y, test_size = 0.25, random_state = 0, shuffle = TRUE)

scores <- cross_validation(split_data[['X_train']], split_data[['y_train']], k = 3, shuffle = TRUE, random_state = 0)

summary_cv(scores)
```
